Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
changing output to word doc

---
title: "Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation"
author: "Team Fresh"
date: "2/24/2020"
output: html_document
---

>>>>

---
title: "Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation"
author: "Team Fresh"
date: "2/24/2020"
output: word_document
---
